Modal Abstractions for Virtualizing Memory Addresses

### 2024-07-10 examples.tex
+

$\specline{ \textsf{entry} \mapsto_{\textsf{id}} \textsf{v} \ast \textsf{entry\_val}_{\textsf{pfn}} \mapsto_{\textsf{id}} \textsf{\_} \ast \forall_{i\in \textssf{0 ... 511} } \ldotp  \textsf{entry\_val }_{\textsf{pfn}} + \texstf{i * 8} \mapsto_{\textsf{id}} \textsf{\_}   \ast \ghostmaptoken{\delta{}s}{\rtv}{\delta} \ast \mathsf{nextpaddr} \in \Xi\setminus \{ \mathsf{entry} \} \} }_{\rtv}$

@@

@@

@@

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}_{\textsf{id}}(\theta,\Xi\setminus \{ \mathsf{entry} \},m)  \ast \textsf{rbp-8} \mapsto_{\textsf{v}} \textsf{entry} \ast \texttt{r8}  \mapsto_{\textsf{r}} \textsf{entry}  \ast \texttt{rdi}  \mapsto_{\textsf{r}} \textsf{entry\_val'}  }_{\rtv}$
$\specline{ \texttt{rbp-16} \mapsto_{\textsf{v}} \textsf{nextpaddr} \ast  \mathsf{nextpaddr} \mapsto_{\textsf{p}} \textsf{w0\_64} \ast \texttt{rax} \mapsto_{\textsf{r}} \textsf{nextpaddr}  }_{\rtv}$

>>>>

$\specline{ \textsf{entry} \mapsto_{\textsf{id}} \textsf{\_} \ast \textsf{entry\_val}_{\textsf{pfn}} \mapsto_{\textsf{id}} \textsf{\_} \ast \ulcorner  \textsf{qfrac} = 1 \land \lnot(\textsf{entry\_present entry\_val}_{\textsf{pfn}})  \urcorner  \ast \ghostmaptoken{\delta{}s}{\rtv}{\delta}  }_{\rtv}$

@@

$\specline{ \forall_{i\in \textssf{0 ... 511} } \ldotp  \textsf{entry\_val }_{\textsf{pfn}} + \texstf{i * 8} \mapsto_{\textsf{id}} \textsf{\_} \ast  \textsf{qfrac} = 1 \land \lnot(\textsf{entry\_present entry\_val }_{\textsf{pfn}} + \texstf{i * 8})  }$

@@

$\specline{ \textsf{entry} \mapsto_{\textsf{id}} \textsf{\_} \ast \textsf{entry\_val}_{\textsf{pfn}} \mapsto_{\textsf{id}} \textsf{\_} \ast \ulcorner  \textsf{qfrac} < 1 \land (\textsf{entry\_present entry\_val}_{\textsf{pfn}})  \urcorner  \ast \ghostmaptoken{\delta{}s}{\rtv}{\delta}  }_{\rtv}$
$\specline{ \forall_{i\in \textssf{0 ... 511} } \ldotp  \textsf{entry\_val }_{\textsf{pfn}} + \texstf{i * 8} \mapsto_{\textsf{id}} \textsf{\_} \ast  \textsf{qfrac} = 1 \land \lnot(\textsf{entry\_present entry\_val }_{\textsf{pfn}} + \texstf{i * 8})  }$

@@
